A Classical Density-Functional Theory for Describing Water Interfaces

### 2012-08-20 papers/water-SAFT/paper.tex
cut redundant citation of same paper Tested everything on node05.

A number of classical density functionals have been developed for
water~\cite{ding1987, Yang1992, yang1994density, gloor2002saft,
  gloor2004accurate, gloor2007prediction, Jaqaman2004, chuev2006,
  clark2006developing, chuev2006,
  lischner2010classical, fu2005vapor-liquid-dft,kiselev2006new,
  blas2001examination}, each of which
captures some of the qualitative behavior of water.  However, each of
these functionals also fail to capture some of water's unique
properties.  For instance, the functional of Lischner \emph{et
  al}\cite{lischner2010classical} treats the surface tension
correctly, but can only be used at room temperature, and thus captures
none of the temperature-dependence of water.  A functional by Chuev
and Skolov\cite{chuev2006} uses an ad hoc modification of FMT that can
predict hydrophobic hydration near temperatures of 298~K, but does not produce a
correct equation of state due to their method producting a high value
for pressure. A number of classical density functionals have recently been produced that are based on
Statistical Associating Fluid Theory (SAFT)\cite{ 
  yu2002fmt-dft-inhomogeneous-associating,
  fu2005vapor-liquid-dft,gloor2002saft,muller2001molecular,
  clark2006developing, gloor2007prediction, gloor2004accurate,
  gross2009density, kahl2008modified, blas2001examination}.  These
functionals are based on a perturbative thermodynamic expansion, and
do reproduce the temperature-dependence of water's properties.

>>>>

A number of classical density functionals have been developed for
water~\cite{ding1987, Yang1992, yang1994density, gloor2002saft,
  gloor2004accurate, gloor2007prediction, Jaqaman2004,
  clark2006developing, chuev2006,
  lischner2010classical, fu2005vapor-liquid-dft,kiselev2006new,
  blas2001examination}, each of which
captures some of the qualitative behavior of water.  However, each of
these functionals also fail to capture some of water's unique
properties.  For instance, the functional of Lischner \emph{et
  al}\cite{lischner2010classical} treats the surface tension
correctly, but can only be used at room temperature, and thus captures
none of the temperature-dependence of water.  A functional by Chuev
and Skolov\cite{chuev2006} uses an ad hoc modification of FMT that can
predict hydrophobic hydration near temperatures of 298~K, but does not produce a
correct equation of state due to their method producting a high value
for pressure. A number of classical density functionals have recently been produced that are based on
Statistical Associating Fluid Theory (SAFT)\cite{ 
  yu2002fmt-dft-inhomogeneous-associating,
  fu2005vapor-liquid-dft,gloor2002saft,muller2001molecular,
  clark2006developing, gloor2007prediction, gloor2004accurate,
  gross2009density, kahl2008modified, blas2001examination}.  These
functionals are based on a perturbative thermodynamic expansion, and
do reproduce the temperature-dependence of water's properties.
